ODGI: understanding pangenome graphs

### 2021-11-09 manuscript/submission/letter.tex
tweaks
make all happy

Dear editors,
%\hfill \break
%\hfill \break

@@

Our description of ODGI is intended to describe a practical modality for working with pangenomes that ODGI implements.
As such, it is largely qualitative and theoretical.
As our focus is primarily conceptual, we have omitted performance based comparisons with the vg toolkit, which is the only similar existing system to ODGI.
However, we do demonstrate that ODGI is capable of efficiently working with large, complex pangenomes.
This high-level focus on the toolkit necessitates the omission of deep algorithmic details that might be of formal interest to the community.
Likewise, there are enough small pieces to the toolkit that a full description of all parts may not be helpful.
We hope that through review we can strike a suitable balance of focus on such detail.

@@

%\hfill \break
\hfill \break

%\begin{flushright}
%\hspace*{100mm}
\indent Sincerely,\\
\hfill \break
\includegraphics[width=0.38\textwidth]{signature_Erik_Garrison.pdf}
\hfill \break
\indent Erik Garrison
%\end{flushright}

>>>>

Dear editors,
\hfill \break
%\hfill \break

@@

Our description of ODGI is intended to present a practical modality for working with pangenomes that ODGI implements.
As such, it is largely qualitative and theoretical.
%As our focus is primarily conceptual, we have omitted performance based comparisons with the vg toolkit, which is the only similar existing system to ODGI.
However, we do demonstrate that ODGI is capable of efficiently working with large, complex pangenomes.
This high-level focus on the toolkit necessitates the omission of deep algorithmic details that might be of formal interest to the community.
Likewise, there are enough small pieces to the toolkit that a full description of all parts may not be helpful.
We hope that through review we can strike a suitable balance of focus on such detail.

@@

\hfill \break

%\begin{flushright}
%\hspace*{100mm}
\indent Sincerely,\\
%\hfill \break
\includegraphics[width=0.34\textwidth]{signature_Erik_Garrison.pdf}
\hfill \break
\indent Erik Garrison
%\end{flushright}
